Minimum Uncertainty JPDA Filters and Coalescence Avoidance for Multiple Object Tracking \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2018-06-09 Journal/JAS Data Association/JAS Data Assoc Reviewer Answers.txt

Thank you for both comments. The actual calculation of an optimal “c” or “a” (in the similarity measure) are beyond the scope of this paper. And yes, there exists a Parento frontier and the choice of “c” depends on the type of scenario (for example, the B1 and B2 results have different cost function parameters). A little more explanation on this is included after eqn (25):

“The estimator gain $K_i$ is selected to minimize the above cost $\mathbf{J}$. By considering similarity to obtain the estimator gain, we mitigate some coalescence at the expense of increasing estimate uncertainty according to the magnitude of $c$. The choice of $c$ depends on the type of scenario and the parameter $a$ composing the similarity cost $J_S$.”

Reviewer #3: “The C-JPDAF is referred to as a ‘coalescence-avoiding optimal JPDAF’.   While I don't disagree that you defined a cost function and optimized it, there is no proof that this correlates to a good filter.  The cost function J_s seems to be completely heuristic.  By simply combing two cost function with a weight parameter, the new cost function in eqn (24) is generally not optimal with respect to either J_P or J_S, so calling it ‘optimal coalescence avoiding’ is not true.”

The C-JPDAF is only optimal with respect to the combined cost, where the $J_S$ component is based off of prior work on multivariate Gaussian similarity, which yields to sharing measurements, and ultimately coalescence. The authors did not see a mathematical method to show that minimizing this weighted cost function yielded a good filter, but showed its performance with numerical simulations.

Reviewer #3: “The C-JPDAF, by virtue of the cost function in eqn (24), seems to define an inherently biased estimator.  The J_S term introduces a bias.  Biases are a very bad property for an estimator.  This bias may also cause the filter to fail completely, and no discussion on how to avoid this is included.”
Reviewer #3: “The C-JPDAF as derived appears to have major flaws involved in cross tagging (aka track swapping).  Cross tagging happens when two objects become identical in the measurement space, implying inherent unobservablity.  This implies that during the unobservability, you cannot distinguish the tracks. The C-JPDAF attempts to solve this problem by adding a repulsive term to the cost function.  It seems to me that if two objects cross over each other similar to Fig (3), this repulsive term may serve to encourage cross tagging.  In general, there may be many unintended consequences of this filter, which is dangerous.”

These are good points. So too does coalescence produce a biased estimator with the JPDAF or the M-JPDAF, and there is no guarantee that cross-tagging will be avoided. The following is added as the second-to-last paragraph of Section 5 to address these issues:

“Furthermore, coalescence serves as a bias to the soft decision data association algorithms, where the bias is toward nearby tracks. The C-JPDAF also has an inherent bias by including $J_S$ from (31), except this bias is away from the nearby tracks. While there is no guarantee that these biases cancel, their opposite effects can reduce estimation error and track swapping. If (25) is poorly tuned such that $J_S$ is too strong, its repulsive nature may yield increased estimation error and track swapping.”

Reviewer #3: “There is no proof that the C-JPDAF solves the coalescence problem.  A heuristic cost function and 6 simulated test cases are not enough proof.”

We never claim that the coalescence problem is solved. This paper presents a method to mitigate some coalescence.

Reviewer #3: “Everything that is claimed as a contribution in this paper is mathematically correct (e.g. a cost function is correctly defined and optimized over). This filter is optimal with respect to a cost function and may avoid coalescence in certain test cases.  However, this filter may also fail in certain test cases, cause problems with cross tagging, and not actually solve coalescence.  If you are convinced my assessment is incorrect, then you must prove these properties mathematically.”

Your assessment is correct.

Reviewer #3: “Results section shows a few test cases and claims them as representative.  Given that the C-JPDAF is completely heuristic, simulation results should be comprehensive, to at least back up numerically that claimed properties of the filter. The work is in filtering which is fundamentally stochastic.  The results need to be run over many different test cases.  Some measure of success, most likely in terms of percent success should be shown.  When does this method break down and how does it fail? If this is to be accepted, Monte Carlo level results are needed to give evidence in support of claims.”

The C-JPDAF is not completely heuristic; it solves an optimization problem, where the cost function itself can be considered heuristic, as many are. This is contrary to other coalescence-avoiding techniques that simply remove possible associations or artificially change estimation parameters known to cause coalescence.

Regarding the Monte Carlo results, running 100 trials of each case with different noise highlighted some important points. These are included under the paragraph “Monte Carlo Results of All Scenarios”.

Technical Detail Comments

Reviewer #3: “Eqn (8), you have R_i as dependent on the object rather than dependent on the measurement.  Because you don't a priori know which objects produce which measurements, and you make no ‘hard decision’, the measurement noise can only be a function of the measurement itself, ‘R_j’”

Note that this is the “a priori innovation covariance matrix”, which has nothing to do with a particular $z_j$, but rather only the expected noise of a correctly associated measurement originating from the $i$-th estimate. The term $R_i$ is indexed with the objects because it might be different among various object estimates, e.g., an object much closer to a sensor might have a measurement with less expected noise than with an object much farther away.

Reviewer #3: “Eqn (10), the notation is very confusing.  Do not use i and j as both global markers, and summation counters in the same equation.”

Thank you for noticing this. The summation counter index is replaced with $l$.

Reviewer #3: “Eqn (11), the e_i is boldface, while up until now, no variable type has been used as bold.  Please use consistent notation.”

The boldface has been removed from this variable.

Reviewer #3: “Eqn (13) and throughout the derivation, random variables don't appear to be correctly handled. e_{ij} is a function of z_j.  z_j is a random variable which means e_{ij} is a random variable.  ~P_i should not be a random variable.”

It is true that $z_j$ and $e_{ij}$ are random variables, but so too is $\tilde P_i$ (see reference [3]), because this positive semi-definite portion of the posterior covariance matrix depends on the innovation spread composed of random variables. This term is specific to soft decision updates only, so this type of term is not found in a nearest neighbor Kalman filter, for example.

Reviewer #3: “Section 4.1: There are some discrepancies between multivariate probability distributions and Gaussian distributions.  You describe Matusita's method as a measure for any two PDFs, but then define it for specifically, Gaussian variables.  Use consistent language.”

The measure is only valid for Gaussian distributions, and both the paper text and figure is updated to reflect that.

Reviewer #3: “In section 4.1, you use the term ‘similarity measure’.  Measure is a mathematical term with a very specific meaning.  Please clarify or use different terminology.”

The term is a “measure” because it is a systematic way of assigning a number to the similarity of Gaussian random variables.

Reviewer #3: “Between Eqn (25) and (26) you make the claim that P_i^+ does not depend on any gain except K_i.  Your posterior distribution does depend on implicitly on previous gains.  Clarify or correct this statement.”

As stated at the beginning of Section 3.2, the remaining analysis takes place at the $k$-th time step. The sentences are combined as:

“…where $P^+_i$ is obtained by (13), dependent on the gain $K_i$ at the current time step.”

Reviewer #3: “I am not convinced the weighting factor, ‘a’, cannot be taken out of eqn (30) and combined with ‘c’.  Same as with ‘c’, a discussion of what ‘a’ should be must be included.”

The weighting factor $a$ is part of a product inside the exponent, so it cannot be easily removed; $a$ serves to change the size and shape of the similarity cost, whereas $c$ only affects the size. The added portion from a previous comment above discusses this briefly:

“The choice of $c$ depends on the type of scenario and the parameter $a$ shaping the similarity cost $J_S$.”

Reviewer #3: “The C-JPDAF appear to have a global minimum, but in 6 dimensional state space it will most likely be difficult to determine.  More discussion on ways to solve this problem would be useful.”

It is difficult to determine. A little more discussion on this with the Monte Carlo simulations is included per your suggestion.

Reviewer #3: “The thorough discussion of Keplarian orbital dynamics around eqn (34-35) is largely unnecessary considering the audience.”

This is true considering the majority of the audience. However, the contributions from this paper are easily extended to other data association problems, such as vision-base tracking of people or automobiles. Because other audiences do not necessarily have an aerospace background, we did not want to alienate this audience from understanding the results.

Additional AE Comments for the Author
“Please provide sufficient detail of the version of the JPDAF considered in this paper, list the assumptions about the detection probability, false measurements, measurement resolution (i.e., can one measurement originate from two objects?), and object size (i.e., can two or more measurements originate from one object?) under which that the M-JPDAF and C-JPDAF are derived, and explain why neither a missed detection model nor a false measurement model is needed for determining the association probability in equation (10).”

To address these issues, the following is revised after equation (11) (formerly 10):

“…where $B=0$ corresponds to rare extraneous measurements and missed detections. When these are prevalent, a fixed value of $B$ found from simulations was shown to perform well in various applications [1]. In this paper, we assume that at most a single measurement may originate from a single object, and missed detections and measurements originating from extraneous clutter are considered insignificant, so $B=0$ is used to determine joint association probability.”

“The statement that the JPDAF is interior to the M-JPDAF needs further analysis. Equation (12) should be re-derived. When K_i is not the optimal gain from the Kalman filter, the covariance or mean square matrix of the estimate given by equation (11) may take a different form than equation (12). For targets described by linear Gaussian systems, if the prior pdf of the state of target i is Gaussian, the posterior pdf of the state of target i is a Gaussian mixture. In the JPDAF, the Gaussian mixture is approximated by a Gaussian pdf, but the two pdfs have the same mean and covariance. Thus, the JPDAF estimate given by equation (11), with K_i the optimal gain from the Kalman filter, is the posterior mean and therefore also the minimum mean square error estimator. Why the posterior mean is worse than the C-JPDAF estimate should be explained.”

<Answer to come>
